\documentclass[12pt,a4paper]{report}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[lining]{ebgaramond}
\usepackage[cmintegrals,cmbraces]{newtxmath}
\usepackage{microtype}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{pdflscape}
\usepackage{float}
\usepackage{enumitem}
\usepackage{makecell}
\graphicspath{{./}}

% Page layout
\geometry{
    left=1.8cm,
    right=1.8cm,
    top=2.2cm,
    bottom=2.2cm
}

% Color definitions
\definecolor{crimson}{RGB}{153, 0, 0}
\definecolor{darkblue}{RGB}{0, 0, 153}

% Hyperlink settings
\hypersetup{
    colorlinks=true,
    linkcolor=crimson,
    urlcolor=crimson,
    citecolor=crimson
}

% Make \textbf default to crimson color
\let\oldtextbf\textbf
\renewcommand{\textbf}[1]{\oldtextbf{\textcolor{crimson}{#1}}}

% Allow line breaks at slashes to prevent overfull hbox
\tolerance=2000
\emergencystretch=2em

% Chapter/section title formatting
\usepackage{titlesec}
\titleformat{\chapter}{\normalfont\huge\bfseries}{}{0pt}{}[\vspace{0.3em}]
\titlespacing*{\chapter}{0pt}{0pt}{14pt}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

\pagestyle{plain}

% ─────────────────────────────────────────────
%  Cover Page
% ─────────────────────────────────────────────
\begin{titlepage}
\centering
\vspace*{3cm}

{\fontsize{28}{34}\selectfont\bfseries DSP in VLSI\par}
\vspace{0.6em}
{\fontsize{20}{26}\selectfont\bfseries Homework 3\par}
\vspace{0.4em}
{\fontsize{16}{22}\selectfont\bfseries Interpolator\par}

\vspace{1.5cm}
\textcolor{crimson}{\rule{0.6\linewidth}{1.2pt}}
\vspace{1.5cm}

{\large\bfseries Student ID}\par
\vspace{0.4em}
{\large M11407439}\par

\vspace{0.8em}

{\large\bfseries Name}\par
\vspace{0.4em}
{\large MING-HONG, LIN}\par

\vspace{2cm}

{\large\bfseries Development Environment}\par
\vspace{0.8em}
\begin{tabular}{rl}
    \textbf{HDL}              & Verilog HDL \\[4pt]
    \textbf{Simulation Tools} & Synopsys VCS and Verdi \\[4pt]
    \textbf{Synthesis Tool}   & Synopsys DC Compiler \\[4pt]
    \textbf{Process}          & TSMC 16nm(ADFP) \\[4pt]
    \textbf{Verification}     & Python \\
\end{tabular}

\vfill

\textcolor{crimson}{\rule{0.6\linewidth}{0.6pt}}\par
\vspace{0.5em}
{\small Due Date: 2026/??/??}

\end{titlepage}

% ─────────────────────────────────────────────
%  Table of Contents
% ─────────────────────────────────────────────
\tableofcontents
\newpage

% ─────────────────────────────────────────────
\chapter{Step 1 — Interpolator Function Verification (Over-Sampled Cases)}
% ─────────────────────────────────────────────

Assume that
\[
    x_1[m] = \cos\!\left(2\pi\!\left(\frac{mT_s}{10T_s}+\frac{\phi}{2}\right)\right)
            + j\sin\!\left(2\pi\!\left(\frac{mT_s}{10T_s}+\frac{\phi}{2}\right)\right),
\]
where $\phi = \mathrm{mod}(d,\,2)$ and $d$ is the last digit of your student ID.
The sampling frequency is 10 times the frequency of the sinusoidal wave.

Please use \textbf{linear interpolator} and \textbf{second-order polynomial
interpolator} to interpolate the sampled waveform in the region of
$10 \le m \le 20$ with $\mu = 0,\tfrac{1}{8},\tfrac{2}{8},\ldots\tfrac{7}{8}$.
Note that you have $x_1[9]$ when you want to interpolate $x_1[10.125]$.

Show the \textbf{real-part} and \textbf{imaginary-part} output waveform
$\hat{x}_1[m+\mu]$ after interpolation for both methods.
In addition, draw the absolute error
$|x_1[m+\mu]-\hat{x}_1[m+\mu]|$
in the region of $10 \le m \le 20$ with
$\mu = 0,\tfrac{1}{8},\tfrac{2}{8},\ldots\tfrac{7}{8}$.
\textbf{(30\%)}

\section{Linear Interpolator}

% [Insert waveform and error figures here]

\section{Second-Order Polynomial Interpolator}

% [Insert waveform and error figures here]

\section{Error Comparison}

% [Insert comparison analysis here]

\newpage

% ─────────────────────────────────────────────
\chapter{Step 2 — Interpolator Function Verification (Typical Cases)}
% ─────────────────────────────────────────────

Assume that
\[
    x_2[m] = 2^{-20}\!\left[\cos\!\left(2\pi\!\left(\frac{mT_s}{4T_s}+\frac{\phi}{3}\right)\right)
            + j\sin\!\left(2\pi\!\left(\frac{mT_s}{4T_s}+\frac{\phi}{3}\right)\right)\right],
\]
where $\phi$ is the same parameter according to your student ID.
The sampling frequency is 4 times the frequency of the sinusoidal wave.

Please use \textbf{linear interpolator} and \textbf{piecewise parabolic interpolator}
to interpolate the sampled waveform in the region of $5 \le m \le 10$ with
$\mu = 0,\tfrac{1}{9},\tfrac{2}{9},\ldots\tfrac{8}{9}$.

Show the \textbf{real-part} and \textbf{imaginary-part} output waveform
$\hat{x}_2[m+\mu]$ after interpolation.
In addition, draw the absolute error
$|x_2[m+\mu]-\hat{x}_2[m+\mu]|$
in the region of $4 \le m \le 8$ with
$\mu = 0,\tfrac{1}{8},\tfrac{2}{8},\ldots\tfrac{7}{8}$.
\textbf{(30\%)}

\section{Linear Interpolator}

% [Insert waveform and error figures here]

\section{Piecewise Parabolic Interpolator}

% [Insert waveform and error figures here]

\section{Error Comparison}

% [Insert comparison analysis here]

\newpage

% ─────────────────────────────────────────────
\chapter{Step 3 — Bit-True Model (BF16)}
% ─────────────────────────────────────────────

Please use \textbf{BF16 format} to realize addition and multiplication.
Write the bit-true model (simulated program in Python) to realize BF16 additions
and multiplication. For simplicity, NaN, infinity, and subnormal numbers are not
handled — if the magnitude is smaller than the smallest normal number, use
\textbf{truncation} to make it become 0. Truncation is also used to avoid
renormalization.

Show the results calculated by your BF16 bit-true model for the following operands.
Express results both in \textbf{decimal} and \textbf{binary} representation
(S = sign bit, E = exponent field, F = fraction field, all in binary).
\textbf{(20\%)}

\section{BF16 Operation Results}

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{cllc}
        \toprule
        & \textbf{Operand 1} & \textbf{Operand 2} & \textbf{Operation} \\
        \midrule
        (a) &
        \makecell[l]{S: 1 \\ E: \texttt{1000\_0011} \\ F: \texttt{0000\_000}} &
        \makecell[l]{S: 0 \\ E: \texttt{1000\_1011} \\ F: \texttt{0000\_011}} &
        Addition \\
        \midrule
        (b) &
        \makecell[l]{S: 1 \\ E: \texttt{0000\_0001} \\ F: \texttt{0000\_011}} &
        \makecell[l]{S: 0 \\ E: \texttt{0000\_0001} \\ F: \texttt{1111\_010}} &
        Addition \\
        \midrule
        (c) &
        \makecell[l]{S: 1 \\ E: \texttt{0000\_0010} \\ F: \texttt{1100\_000}} &
        \makecell[l]{S: 0 \\ E: \texttt{0111\_1100} \\ F: \texttt{0000\_110}} &
        Multiplication \\
        \midrule
        (d) &
        \makecell[l]{S: 0 \\ E: \texttt{0110\_0011} \\ F: \texttt{1011\_110}} &
        \makecell[l]{S: 0 \\ E: \texttt{1001\_0011} \\ F: \texttt{0101\_000}} &
        Multiplication \\
        \bottomrule
    \end{tabular}
    \caption{BF16 operands and operations.}
    \label{tab:bf16-ops}
\end{table}

% [Insert computed results table here]

\newpage

% ─────────────────────────────────────────────
\chapter{Step 4 — Performance Degradation by Finite Precision}
% ─────────────────────────────────────────────

Please analyze the error of the \textbf{second-order interpolator} if its arithmetic
operations are changed to BF16 by using the bit-true model.

Draw the figures indicating the difference of interpolated results caused by data
format for outputs $\hat{x}_1[m+\mu]$ in the region of $10 \le m \le 20$
with $\mu = 0,\tfrac{1}{8},\tfrac{2}{8},\ldots\tfrac{7}{8}$.
\textbf{(10\%)}

\section{BF16 vs. Double-Precision Error Analysis}

% [Insert error figures comparing BF16 and double-precision results here]

\newpage

% ─────────────────────────────────────────────
\chapter{Step 5 — Hardware Reduction}
% ─────────────────────────────────────────────

According to Fig.~4 of the assignment, draw the \textbf{entire block diagram}
of the original piecewise parabolic interpolator of Farrow structure.
Then, observe the block diagram to identify any reduction that can be achieved.

List \textbf{at least two design approaches} (original and simplified) related
to hardware sharing for saving D flip-flops, multipliers, or adders.
Draw the \textbf{revised block diagram} of the implementation to be used.

\begin{itemize}
    \item Draw complete block diagram of the first version (5\%)
    \item Show the hardware sharing version — datapath precision must remain BF16 (10\%)
    \item Draw block diagram after improvement (5\%)
    \item Indicate the critical path (5\%)
\end{itemize}

\section{Original Block Diagram (Farrow Structure)}

% [Insert original block diagram figure here]

\section{Hardware Sharing Approaches}

% [Describe at least two design approaches here]

\section{Revised Block Diagram After Reduction}

% [Insert revised block diagram figure here]

\section{Critical Path Analysis}

% [Indicate and explain the critical path here]

\newpage

% ─────────────────────────────────────────────
\chapter{Step 6 — Implementation}
% ─────────────────────────────────────────────

Please write Verilog to implement the \textbf{second-order interpolator} of
Farrow structure using \textbf{BF16 arithmetic units} after hardware reduction.
Insert D flip-flops at inputs and outputs.

Note: The input to be interpolated changes \textbf{every 8 clock cycles};
the $\mu$ value changes \textbf{every clock cycle}.

\section{Behavior Simulation}

Show the timing diagram of behavior simulation for the
\textbf{first 8} ($\mu = 0,\tfrac{1}{8},\ldots\tfrac{7}{8}$) and
\textbf{last 8} ($\mu = 0,\tfrac{1}{8},\ldots\tfrac{7}{8}$)
interpolated outputs of $\hat{x}_1[m+\mu]$
in the region of $10 \le m \le 20$.

Show the \textbf{real-part} and \textbf{imaginary-part} error of hardware
implementation results compared to the double-precision results.
\textbf{(30\%)}

% [Insert behavior timing diagram (first 8 and last 8 outputs) here]
% [Insert real-part and imaginary-part error figures here]

\newpage

\section{Timing Report and Constraint}

Show your \textbf{timing report} to verify the critical path of the block diagram
in Step~5. \textbf{(10\%)}
List your \textbf{timing constraint} for post-synthesis simulation. \textbf{(5\%)}

% [Insert timing report screenshot here]

\begin{table}[H]
    \centering
    \begin{tabular}{lc}
        \toprule
        \textbf{Parameter} & \textbf{Value (ns)} \\
        \midrule
        Clock Period                  & \\
        Clock Uncertainty             & \\
        Clock Latency                 & \\
        Input / Output Maximum Delay  & \\
        \bottomrule
    \end{tabular}
    \caption{Timing constraint settings.}
    \label{tab:timing-constraint}
\end{table}

\newpage

\section{Post-Synthesis Simulation}

Show the timing diagram of \textbf{post-synthesis simulation} for the
first 8 and last 8 interpolated outputs of $\hat{x}_1[m+\mu]$
in the region of $10 \le m \le 20$.

Show the \textbf{real-part} and \textbf{imaginary-part} error of post-synthesis
hardware outputs compared to the double-precision results. \textbf{(20\%)}

% [Insert post-synthesis timing diagram (first 8 and last 8 outputs) here]
% [Insert real-part and imaginary-part error figures here]

\newpage

\section{BF16 Bit-True Model vs. Verilog Output Verification}

Construct the \textbf{BF16 bit-true model} following the architecture after
hardware improvement. Depict the \textbf{real-part} and \textbf{imaginary-part}
errors of interpolated outputs $\hat{x}_1[m+\mu]$ between the Verilog outputs
and the bit-true model in the region of $10 \le m \le 20$
with $\mu = 0,\tfrac{1}{8},\tfrac{2}{8},\ldots\tfrac{7}{8}$. \textbf{(20\%)}

% [Insert real-part and imaginary-part error figures comparing Verilog vs. bit-true model here]

\end{document}
