\documentclass[12pt,a4paper]{report}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[lining]{ebgaramond}
\usepackage[cmintegrals,cmbraces]{newtxmath}
\usepackage{microtype}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{pdflscape}
\usepackage{float}
\usepackage{enumitem}
\graphicspath{{./}}

% Page layout
\geometry{
    left=2.5cm,
    right=2.5cm,
    top=2.5cm,
    bottom=2.5cm
}

% Color definitions
\definecolor{crimson}{RGB}{153, 0, 0}
\definecolor{darkblue}{RGB}{0, 0, 153}

% Hyperlink settings
\hypersetup{
    colorlinks=true,
    linkcolor=crimson,
    urlcolor=crimson,
    citecolor=crimson
}

% Allow line breaks at slashes to prevent overfull hbox
\tolerance=2000
\emergencystretch=2em

% Chapter/section title formatting
\usepackage{titlesec}
\titleformat{\chapter}{\normalfont\huge\bfseries}{}{0pt}{}[\vspace{0.3em}]
\titlespacing*{\chapter}{0pt}{30pt}{20pt}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

\pagestyle{plain}

% ─────────────────────────────────────────────
%  Cover Page
% ─────────────────────────────────────────────
\begin{titlepage}
\centering
\vspace*{3cm}

{\fontsize{28}{34}\selectfont\bfseries DSP in VLSI\par}
\vspace{0.6em}
{\fontsize{20}{26}\selectfont\bfseries Homework 2\par}
\vspace{0.4em}
{\fontsize{16}{22}\selectfont\bfseries Digital Filter\par}

\vspace{1.5cm}
\textcolor{crimson}{\rule{0.6\linewidth}{1.2pt}}
\vspace{1.5cm}

{\large\bfseries Student ID}\par
\vspace{0.4em}
{\large M11407439}\par

\vspace{0.8em}

{\large\bfseries Name}\par
\vspace{0.4em}
{\large MING-HONG, LIN}\par

\vspace{2cm}

{\large\bfseries Development Environment}\par
\vspace{0.8em}
\begin{tabular}{rl}
    \textbf{HDL}              & Verilog HDL \\[4pt]
    \textbf{Simulation Tools} & Synopsys VCS and Verdi \\[4pt]
    \textbf{Synthesis Tool}   & Synopsys DC Compiler \\[4pt]
    \textbf{Process}          & TSMC 16nm (ADFP) \\[4pt]
    \textbf{Verification}     & Python \\
\end{tabular}

\vfill

\textcolor{crimson}{\rule{0.6\linewidth}{0.6pt}}\par
\vspace{0.5em}
{\small Due Date: 2026/04/08}

\end{titlepage}

% ─────────────────────────────────────────────
%  Table of Contents
% ─────────────────────────────────────────────
\tableofcontents
\newpage

% ─────────────────────────────────────────────
%  Question 1
% ─────────────────────────────────────────────
\chapter{Question 1 — Filter Analysis}

Please use Matlab/Python to draw the \textbf{impulse response} and
\textbf{frequency response} (containing magnitude and phase) of the 25-tap
sinc-based FIR filter. Use dB scale for magnitude and radian for phase versus
normalized frequency. The x-axis must be marked with the correct label.
\textbf{(20\%)}
Please explain whether the filter is high-pass, band-pass or low-pass and why.
\textbf{(5\%)}

Draw the time-domain input and output waveforms after feeding 144 input
samples $x[n] = \sin\!\left(-\tfrac{2\pi n}{128}\right) - \cos\!\left(\tfrac{2\pi n}{4}\right)$,
$0 \le n \le 143$, and observe the filtering effect.
\textbf{(20\%)}

\section{Impulse Response}

\section{Frequency Response}

\section{Filter Type Explanation}

\section{Time-Domain Input/Output Waveforms}

% ─────────────────────────────────────────────
%  Question 2
% ─────────────────────────────────────────────
\chapter{Question 2 — Quantization}

Please use \textbf{direct form} to implement the 25-tap FIR filter. Decide the
word-lengths of each data path after additions and multiplications so that the
RMSE error between the fixed-point output and the floating-point output is less
than $2^{-a}$. If $p = 0$, $a = 12$; otherwise $a = 11$, where
$p = \mathrm{mod}(d_1, 2)$ and $d_1$ is the last digit of your student ID.

To show how you determine the word-length, scan the quantization error versus
word-lengths from 9 bits to 15 bits and mark the final word-length settings in
the block diagram. \textbf{(20\%)}

Draw the fixed-point output of the time-domain signal and compare to the
floating-point output. \textbf{(10\% + 10\%)}
Show the frequency response of the fixed-point direct-form FIR filter and
compare the magnitude error in passband (within 3\,dB bandwidth), expressed in
dB. \textbf{(10\% + 5\%)}

\section{Word-Length Determination}

\begin{enumerate}[label=\alph*.]
    \item Output error versus input word-lengths.
    \item Output error versus coefficient word-lengths (input word-length fixed to selected setting).
    \item Output error versus word-lengths after multiplication (input and coefficient word-lengths at desired value).
    \item Output error versus word-lengths after addition (fixed-point representations used for previous three signals).
\end{enumerate}

\section{Fixed-Point Output vs.\ Floating-Point Output}

\section{Frequency Response of Fixed-Point Filter}

\section{Magnitude Error in Passband}

% ─────────────────────────────────────────────
%  Question 3
% ─────────────────────────────────────────────
\chapter{Question 3 — Direct Form Implementation \& Synthesis}

Please implement the \textbf{direct form} FIR filter using the word-lengths
decided in Question~2. Add D flip-flops at input port $x[n]$ and output port
$y[n]$. Find out the critical path, set a proper timing constraint to achieve
the maximal operating frequency, and check the post-\textbf{SYNTHESIS}
simulation results.

Print out the behavior timing diagram for the first 20 and last 20 samples,
and show the errors between hardware outputs and Matlab floating-point results.
\textbf{The latency is not constrained. (10\% + 10\%)}

Paste the timing report of the critical path, show the numbers of adders and
multipliers, and list the timing constraint to achieve the highest operating
frequency. \textbf{(5\% + 5\%)}

Print out the post-\textbf{SYNTHESIS} timing diagram for the first 20 and last
20 samples, and show the post-synthesis vs.\ Matlab floating-point errors.
\textbf{(10\% + 10\%)}

\section{Behavior Simulation Timing Diagram}

\section{Hardware vs.\ Matlab Error}

\section{Critical Path Report}

\section{Timing Constraint \& Maximum Operating Frequency}

\section{Post-Synthesis Timing Diagram}

\section{Post-Synthesis vs.\ Matlab Error}

% ─────────────────────────────────────────────
%  Question 4
% ─────────────────────────────────────────────
\chapter{Question 4 — 2X Speedup via Parallel Processing}

Achieve a 2X speedup by using 2-level parallel processing to accelerate
throughput. Set the input/output style as \texttt{FilterIn0}/\texttt{FilterIn1}
and \texttt{FilterOut0}/\texttt{FilterOut1}.
\textbf{\textcolor{crimson}{Generate $y[0]$ to $y[143]$ within
$T_{\mathrm{out}}/2$.}}
Evaluate functionality correctness and successful speedup, and compare the
resource utilization before and after speedup.

Show that \textbf{\textcolor{crimson}{$y[0]$ to $y[143]$ can be generated
within $T_{\mathrm{out}}/2$}} in the behavior timing diagram. Draw the block
diagram and indicate your critical path. \textbf{(15\%)}
Show your synthesis max delay report to verify your explanations. \textbf{(5\%)}

Show the post-\textbf{SYNTHESIS} simulation results for the first 20 and last
20 samples and indicate why throughput is doubled. \textbf{(10\%)}
Show the errors of post-synthesis outputs vs.\ Matlab floating-point results.
\textbf{(10\%)}
Show the area (resources) before and after speedup from the synthesis report.
\textbf{(10\%)}

\section{Behavior Timing Diagram — $y[0]$ to $y[143]$ within $T_{\mathrm{out}}/2$}

\section{Block Diagram \& Critical Path}

\section{Synthesis Max Delay Report}

\section{Post-Synthesis Simulation \& Throughput Explanation}

\section{Post-Synthesis vs.\ Matlab Error}

\section{Area Comparison Before \& After Speedup}

\end{document}
